A Formal Model of Checked C

### 2023-04-22 sandp23/formal.tex
update.

This section describes our formal model of \systemname, called
\lang, making precise its syntax, semantics, and type system,
as well as \systemname’s meta-theories, including the type preservation, non-exposure, and clean separation theorems.
One thing worth noting is that \lang and its meta-theories are built and verified, despite the underling sandbox mechanisms,
i.e., both implementing both separate heap and WASM sandboxes result in the same properties.

>>>>

This section describes our formal model of \systemname, called
\lang, making precise its syntax, semantics, and type system,
with the \systemname’s meta-theories shown in \Cref{}, including the type preservation, non-exposure, and clean separation theorems.
One thing worth noting is that \lang and its meta-theories are built and verified, despite the underling sandbox mechanisms,
i.e., both implementing both separate heap and WASM sandboxes result in the same properties.
